---
title: ""
format: 
  html:
    theme: journal
    css: custom.css
editor: visual
knitr:
  opts_chunk: 
    echo: false
    message: false
    warning: false
---

```{r}
#| include: false
#| cache: false
googlesheets4::gs4_deauth()
cv_url <- Sys.getenv("cv_url_en")

cv <- googlesheets4::read_sheet(cv_url)
```

:::::: columns
::: {.column width="25%"}
<center><a href='https://www.linkedin.com/in/adihara/' target='_blank'> ![](https://avatars.githubusercontent.com/u/140970817?s=400&u=0f773ff57a45dce22a719d9d6506524c44f06c7a&v=4){style="border-radius: 50%;"}</center>

</a>

### Contact

<center><span style="font-size: 1.5em;"> <a href='https://www.linkedin.com/in/adihara/' target='_blank'><i class="fa fa-home"></i></a> <a href='https://github.com/adihara' target='_blank'><i class="fa-brands fa-github"></i></a> <a href='mailto:adiharalima@gmail.com'><i class="fa fa-envelope"></i></a></center>

</span>

Hello, my name is Adhara! I'm a Senior Data Analyst at one of Brazil's six reference hospitals since 2021. I manage and analyze data for projects under the Institutional Development Support Program of the Unified Health System (PROADI-SUS). I'm dedicated to continuous learning and development to effectively contribute to scientific research and projects. Currently, I'm pursuing an MBA in Data Science with the aim of expanding my professional possibilities.

### Presentations

<i class="fas fa-chalkboard-teacher"></i> [Data Analysis and the REDCap Platform](https://www.linkedin.com/events/an-lisededadoscomaplataformared7211506271647113216/theater/).

<i class="fas fa-chalkboard-teacher"></i> [Optimizing Data Science Work Using REDCap, Quarto, and Power BI Integrated via API.](https://accamargo.iweventos.com.br/evento/nfcc2023/trabalhosaprovados/naintegra/4317)

<i class="fas fa-chalkboard-teacher"></i> [R Software Course - Module 1](https://redcap.bp.org.br/surveys/?s=9M3NWMNEAP)

### Languages

**Portuguese:** Native <br> **English:** Proficient

### Grants

<i class="far fa-star"></i> [CAPES](https://www.gov.br/capes/pt-br). Master's Scholarship - 2019-2021.

### Programming skills

<i class="fab fa-r-project"></i> `R` <br> <i class="fab fa-python"></i>`Python` <br> <i class="fab fa-markdown"></i> `RMarkdown / Quarto` <br> <i class="fab fa-github"></i> `GitHub` <br> <i class="fa-solid fa-database"></i> `REDCap` <br>
:::

::: {.column width="5%"}
:::

::: {.column width="70%"}
<!-- Functions -->

```{r}
col_br <- function(col){
    dplyr::if_else(
      !is.na(col) & col != "N/A|NA", 
      paste0(col, ""),
      ""
    )
}

col_br_loc <- function(col){
    dplyr::if_else(
      !is.na(col) & col != "N/A|NA", 
      paste0('<i class="fa-solid fa-location-dot"></i>', col),
      ""
    )
}

create_section <- function(cv_data, section_name){
  cv_data |>
    dplyr::mutate(in_resume = as.character(in_resume),
                  end = tidyr::replace_na(end, 9999),
                  loc = dplyr::if_else(loc == "Online", "Online", loc)) |>
    dplyr::filter(in_resume %in% c("TRUE", "VERDADEIRO"), section == section_name) |>
    dplyr::select(section:description_1) |>
    dplyr::arrange(desc(end), desc(start)) |>
    dplyr::mutate(
      date =
        dplyr::case_when(
          end == 9999 ~ glue::glue("Current <br> | <br> {start}"),
          end != start ~ glue::glue("{end} <br> | <br> {start}"),
          end == start ~ glue::glue("{end}"),
          TRUE ~ ""
        ) ,
      .before = everything()
    ) |>
    dplyr::mutate(
      main_text =
        glue::glue(
          "**{title}** <br> {col_br(institution)} {col_br(description_1)} <br> <i class='fa-solid fa-location-dot'></i>  {loc} ")
    )|>
    dplyr::select(-c(start, end, section, title, institution, loc, description_1)) |>
    gt::gt() |>
    gt::fmt_markdown(columns = c(date, main_text)) |> 
    gt::tab_options(column_labels.hidden = TRUE, table.width = gt::pct(100)) |> 
    gt::cols_align(align = "left", columns = main_text) |> 
    gt::cols_width(date ~ gt::pct(10))
}
```

<!-- Main content -->

# Adhara Brandão Lima Vanhoz

## <i class="fa-solid fa-suitcase"></i> Work

```{r}
create_section(cv, "working_experience")
```

## <i class="fas fa-book"></i> Courses

```{r}
create_section(cv, "short_courses")
```

## <i class="fa-solid fa-newspaper"></i> Publications

```{r}
create_section(cv, "scientific_journals")
```

## <i class="fa-solid fa-graduation-cap"></i> Education

```{r}
create_section(cv, "education")
```

<p class="small">

Resume made with [Quarto](https://quarto.org/). Last updated on `r format.Date(Sys.Date(), "%b %d, %Y")`. <br> Code available on <i class="fa-brands fa-github"></i> [GitHub](https://github.com/adihara). <br>License: [CC BY-SA 2.0](https://creativecommons.org/licenses/by-sa/2.0/).

</p>
:::
::::::

```{=html}
<script src="https://kit.fontawesome.com/1bb720cc6f.js" crossorigin="anonymous"></script>
```
